---
title: "Sentiment analysis"
author: "Astrid Rybner"
date: "14/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this code sentiment analysis is conducted using the Sentida package. 
Additionally, the development in sentiment over time is plotted using the gganimatepackage. 

```{r}
# load packages 
library(pacman)
p_load(rlist, Sentida, ggplot2, tidyverse, gganimate)

# set theme 
theme_set(theme_bw()) 

# load data
tweets_before <- read.csv("tweets_before.csv")
tweets_after <- read.csv("tweets_after.csv")

```

## Creating functions for data cleaning and summary 

1. The sentiment_func calculates the total sentiment per tweet and add this value in a new column.

2. The date_func cleans the date column (created_at) and make it into date format, so it can be used in the gganimate plots and returns a dataframe where the column has been cleaned. 

3. The mean_sentiment_pr_day calculates the mean sentiment per unique date in the dataset

```{r}

# sentiment function 
sentiment_func <- function(df){
  sentiment <- c()
  for (i in df$full_text) {
    l = sentida(i, output = "total")
    sentiment = list.append(sentiment, l)
  }
  df <- cbind(df,sentiment)
  return(df)
}


# date format function
date_func <- function(df){
  df$created_at <- str_replace_all(df$created_at, "\\ .*", "")
  df$created_at <- str_replace_all(df$created_at, "2020-", "20-")
  df$created_at <-  as.Date(df$created_at)
  return(df)
  }

# get average sentiment pr unique dates 
mean_sentiment_pr_day =
  function(df){
   summary = df %>% group_by(created_at) %>% summarise(mean_sentiment=mean(sentiment),day=min(created_at)) %>% select(-created_at)
  return(summary)
   }

```


## Getting only tweets with the hashtags #dkgreen and #dkpol (before and after the chosen date 5/5)

```{r}
#dkgreen before
dkgreen_before <- filter(tweets_before, dkgreen=="True")

#dkgreen after
dkgreen_after <- filter(tweets_after, dkgreen=="True")

#dkpol before
dkpol_before <- filter(tweets_before, dkpol=="True")

#dkpol after
dkpol_after <- filter(tweets_after, dkpol=="True")

```

## Applying functions to the four datasets 
```{r}

dkgreen_before <- dkgreen_before %>% sentiment_func() %>% date_func() 

dkgreen_after <- dkgreen_after %>% sentiment_func() %>% date_func()

dkpol_before <- dkpol_before %>% sentiment_func() %>% date_func()

dkpol_after <- dkpol_after %>% sentiment_func() %>% date_func()

```
## Getting mean sentiment scores per unique date in a summary dataframe

```{r}

dkgreen_before_sum <- dkgreen_before %>% mean_sentiment_pr_day()
dkgreen_after_sum <- dkgreen_after %>% mean_sentiment_pr_day()
dkpol_before_sum <- dkpol_before %>% mean_sentiment_pr_day()
dkpol_after_sum <- dkpol_after %>% mean_sentiment_pr_day()

```

## Making animated plots

```{r, echo=FALSE}
anim1 <- ggplot(dkgreen_before_sum, aes(day, mean_sentiment))+geom_line()
anim1 + transition_states(day, 
                         transition_length = 1,
                         state_length = 1)+
                        transition_reveal(day)+
                        labs(x="Date", y="Sentiment Score", title = "#dkgreen before 5/5 2020")
```


```{r, echo=FALSE}
anim2 <- ggplot(dkgreen_after_sum, aes(day, mean_sentiment))+geom_line()
anim2 + transition_states(day, 
                          transition_length = 1,
                          state_length = 1)+
  transition_reveal(day)+
  labs(x="Date", y="Sentiment Score", title = "#dkgreen after 5/5 2020")
```


```{r, echo=FALSE}
anim3 <- ggplot(dkpol_before_sum, aes(day, mean_sentiment))+geom_line()
anim3 + transition_states(day, 
                          transition_length = 1,
                          state_length = 1)+
  transition_reveal(day)+
  labs(x="Date", y="Sentiment Score", title = "#dkpol before 5/5 2020")
```


```{r, echo=FALSE}
anim4 <- ggplot(dkpol_after_sum, aes(day, mean_sentiment))+geom_line()
anim4 + transition_states(day, 
                          transition_length = 1,
                          state_length = 1)+
                          transition_reveal(day)+

    labs(x="Date", y="Sentiment Score", title = "#dkpol after 5/5 2020")
```





